rftdoi
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/ropenscilabs/rftdoi.svg?branch=master)](https://travis-ci.org/ropenscilabs/rftdoi)
[![codecov.io](https://codecov.io/github/ropenscilabs/rftdoi/coverage.svg?branch=master)](https://codecov.io/github/ropenscilabs/rftdoi?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/grand-total/rftdoi?color=2ECC71)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/rftdoi)](https://cran.r-project.org/package=rftdoi)


`rftdoi` is a client for interacting with <https://ftdoi.org>

## Installation

Development version

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropenscilabs/rftdoi")
```

```{r}
library('rftdoi')
```

## Heartbeat - list routes

```{r}
ftd_heartbeat()
```

## Contributors

* Scott Chamberlain [@sckott](https://github.com/sckott)

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/rftdoi/issues).
* License: MIT
* Get citation information for `rftdoi` in R doing `citation(package = 'rftdoi')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
